---
title: "HW 6"
author: "Malvika Venkataraman"
date: "12/2/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
```

# Problem 1
```{r}
birthweight = read_csv("./birthweight.csv") %>%
  janitor::clean_names() %>%
  drop_na() %>%
  mutate(
    babysex = factor(babysex),
    frace = factor(frace),
    malform = factor(malform),
    mrace = factor(mrace)
  )

str(birthweight)
#View(birthweight)
```

## Model
```{r}
model_init <- lm(bwt ~., data = birthweight)
step(model_init, direction = "backward")
```

final model
```{r}
model_back = lm(bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight)
```

plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.
```{r}
birthweight %>%
  add_residuals(model_back) %>%
  add_predictions(model_back) %>%
  ggplot(aes(x = pred, y = resid)) + geom_point(alpha = .3) +
  labs(title = "Residuals vs. Fitted Values")
```

```{r}
cv_df = crossv_mc(birthweight, 100) %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble),
    backwards_mod = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
    mod_main_effect = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_interaction = map(train, ~lm(bwt ~ bhead + blength + babysex 
                                     + bhead * blength 
                                     + bhead * babysex 
                                     + blength * babysex 
                                     + bhead * blength * babysex, data = .x)), 
    rmse_backwards_mod = map2_dbl(backwards_mod, test, ~rmse(model = .x, data = .y)),
    rmse_mod_main_effect = map2_dbl(mod_main_effect, test, ~rmse(model = .x, data = .y)),
    rmse_mod_interaction = map2_dbl(mod_interaction, test, ~rmse(model = .x, data = .y)))
  
```

```{r}
cv_df %>%
  select(starts_with("rmse")) %>%
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_") %>%
  ggplot(aes(x = model, y = rmse)) + geom_violin() +
  labs(title = "RMSE for Cross-Validated Models", x = "Model Type", y = "RMSE")
```

# Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

The boostrap is helpful when you’d like to perform inference for a parameter / value / summary that doesn’t have an easy-to-write-down distribution in the usual repeated sampling framework. We’ll focus on a simple linear regression with tmax as the response and tmin as the predictor, and are interested in the distribution of two quantities estimated from these data:

```{r}
#regression model
lm(tmax ~ tmin, data = weather_df) %>%
  broom::tidy() %>%
  knitr::kable(digits = 3)
```


Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. 




Plot the distribution of your estimates, and describe these in words. Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂ 2 and log(β̂ 0∗β̂ 1). Note: broom::glance() is helpful for extracting r̂ 2 from a fitted regression, and broom::tidy() (with some additional wrangling) should help in computing log(β̂ 0∗β̂ 1).


